
\begin{acknowledgements}      
First, I would like to express my greatest gratitude to my supervisor, Dr.~Kwan-Yee Kenneth Wong, for his continuous support, thoughtful comments, and encouragement throughout my PhD study. Dr.~Wong's supervision helped me start my research in computer vision. I am very grateful for his efforts in both my research and life.

I was lucky to work with my collaborators, and would like to thank them for their invaluable advice and help:
Dr.~Kai Han for all my three projects (Chapter 1, Chapter 2, and part of Chapter 3);
Dr.~Boxin Shi and Prof.~Yasuyuki Matsushita for my second and third projects (Chapter 2 and Chapter 3);
Dr.~Michael Weather for my third project (part of Chapter 3).
In particular, part of my third project was done during my internship at Matsushita Lab in Osaka Univeristy, hosted by Prof.~Yasuyuki Matsushita.

I would like to show my sincere thanks to my colleagues and friends: Dr.~Xiaolong Zhu, Dr.~Xiao Tan, Dr.~Kai Han, Dr.~Wei Liu, Mr.~Chaofeng Chen, Mr.~Zhenfang Chen, Ms.~Jingjing Zhang, Ms.~Bingbin Liu, Mr.~Huiquan Zhou, and Ms.~Wenqi Yang, for their infectious enthusiasm in helping me in both studying and living.
    I also feel grateful for my friends Dr.~Miaomiao Liu, Dr.~Zhanghui Kuang, Dr.~Xuhui Jia, Dr.~Hao Zhou, Dr.~Xingdou Fu, Dr.~Guanbin Li, Dr. Zhen Li, Dr.~Weifeng Ge, and Dr.~Chaowei Fang.

In the summer of 2019, I was fortunate to have an internship at Matsushita Lab in Osaka University. I would like to thank Prof.~Yasuyuki Matsushita, Dr.~Michael Weather, Mr.~Heng Guo, Mr.~Xu Cao, Mr.~Feiran Li, Mr.~Hiroaki Santo, Mr.~Kenji Enomoto, and Mr.~Zhuoyu Yang for their help in both my research and living in Osaka.

I would like to express my heartfelt gratitude to The University of Hong Kong Foundation for Educational Development and Research (‘HKU Foundation’) for its generous support for my research studies in HKU.

Last, I want to thank my parents and beloved one Huijun Li for their unconditional love, support, and trust.

\end{acknowledgements}
